---
title: "Understanding Moves Toward Immigration Populism"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(primer.data)
library(rstanarm)

# Consider someone whose att_end at the end of the experiment is 1 or more units
# greater than their att_start. They become more conservative on immigration
# issues. Consider such people to have made a meaningful move toward immigration
# populism. Let's use `move_to_pop` as a new variable, defined as TRUE for such
# people. We are interested to see if two variables might be associated with
# move_to_pop: treatment and age.

x <- trains %>% 
  mutate(move_to_pop = ifelse(att_end >= att_start + 1, TRUE, FALSE)) %>% 
  select(move_to_pop, treatment, age)
```

#Wisdom

What is the causal effect of the treatment on the probability of becoming more populist?

-The inquiry question does not specify the exact population we are studying (do we care about children? non-American residents/travellers)
- Be cautious about generalizing
Is our sample population of people in 2012 representative of the general population of in 2021?
- People at trains stations may be of certain demographic (age, race, income, etc)
-Train stations selected in MA, which is a liberal state
-Study conducted in 2012, but we want to predict the probability and treatment on people in 2021

#Justice

- We have 3 parameters: treatment, control, and error
-MAD_SD is a more specialized term (Median Absolute Dev)
-SD also a measure of spread
-We use MAD_SD because it's more robust to outliers

#Courage
- Fit the model with stan_glm()

```{r}

fit_1 <- stan_glm(data = x,
                  formula = move_to_pop ~ treatment,
                  family = binomial,
                  seed = 76,
                  refresh = 0)
fit_1

```

```{r}
newobs <- tibble(treatment = c("Control", "Treated"))

posterior_epred(fit_1,
                newdata = newobs) %>%
  as_tibble() %>%
  mutate(ate = `2` - `1`)
```
```{r}

newobs2 <- tibble(treatment = c(rep("Treated", 25)))
newobs2
posterior_predict(fit_1,
                  newdata = newobs2) %>%
  as_tibble() %>%
  mutate_all(as.numeric) %>%
  rowwise() %>%
  mutate(total = sum(c_across())) %>%
  ggplot(aes(x = total)) +
  geom_histogram(aes(y = after_stat(count/sum(count))),
                   bins = 100) +
    scale_x_continuous(labels = scales::number_format(accuracy = 1)) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) 


```


